BIP Architectures and Open pNets

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
shorter affiliation
change les alpha en nom des dandling ports un peu partout... nouveau dessin de l'automate resultat en section 7.

\noteLH{a pred is a g a post is a u (modified macros!)}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of an open pNets is expressed as an open automaton, i.e., an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
 state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  \todoEM{Commenter...
  Questions: les $\alpha$ n'apparaissent pas dans l'archi Bip; la
  synchro des initialisations non plus... OT3 est un peu plus facile a
  expliquer (;-).}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. Two of its possible open-transitions are:

@@

 \smallskip
$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
$
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
  $

@@

The second one, $OT_3$, correspond to the firing of the connector
$''tick, fail, fail''$, with the hole B performing action $fail$......
\end{example}

It is important to understand that the red dotted rule expresses an implication but at a different logical level compared to  a normal 
inference rule. 
 The open transition is  a logical implication that uses a simple logic with the 
 expressive power  given by the predicate algebra (it must include logical 
 propositions and equality). We differentiate classical (black) inference rules that use 
 an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
 mechanically.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOpenAut}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{FailureTimerOA}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

12 open transitions... Comments on the predicates ???

Should list some temporal logic properties....

@@

\small\begin{verbatim}
FailureTimerArchi
--------------------
SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
SV2 SVs: <timeout, timeout, _, ask>-->alpha2
SV3 SVs: <_, reset, _, reset>-->alpha3
SV4 SVs: <init, init, _, _>-->alpha4
pLTS: Timer
- Transition: t0---init-->t1, { t := 0 z := TopInt}
- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
- Transition: t1---cancel(false)-->t1, {}
- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
- Variable: t, State: t1, Value(s) = 0,0,(t+1),
- Variable: z, State: t1, Value(s) = TopInt,z1,
pLTS: Failure
- Transition: s0---init-->s1, { zone := minZone,maxZone}
- Transition: s1---timeout-->s1, {}
- Transition: s1---resume(false)-->s1, {}
- Transition: s1---fail(zone, false)-->s1, {}
- Transition: s1---fail(zone, true)-->s2, {}
- Transition: s2---fail(zone, false)-->s2, {}
- Transition: s2---resume(false)-->s2, {}
- Transition: s2---resume(true)-->s1, {}
- Transition: s2---timeout-->s3, {}
- Transition: s3---fail(zone, false)-->s3, {}
- Transition: s3---resume(false)-->s3, {}
- Transition: s3---reset-->s1, {}
- Variable: zone, State: s1, Value(s) = minZone,maxZone,
Holes: B
Holes: E

INFO  BIPArchFailureTimerMax_LTF3 -
       {t0---init-->t1, s0---init-->s1},   {},  [true],
       {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----alpha4----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)
         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT5 ------------------------------------------------------------
        <t1_s1>-----alpha2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
       {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT9 ------------------------------------------------------------
        <t1_s2>-----alpha2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----alpha0----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----alpha1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
    OT12 ------------------------------------------------------
        <t1_s3>-----alpha3----><t1_s1>

@@

$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
$
\medskip

$  OT_2  = \openrule
{\{B\mapsto fail(b0)\},\\
  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
  \{z:=z1\} }
{\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{11}}
$
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
  $
  \medskip

  $  OT_4  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2
    \{\}  }
  {\ostate{11} \OTarrow{\underline{\alpha_1}} \ostate{11}}
  $
  \medskip

  $  OT_5  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\}  }
  {\ostate{11} \OTarrow{\underline{\alpha_2}} \ostate{11}}
  $
  \medskip

  $  OT_7  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{12}}
  $
  \medskip

  $  OT_8  = \openrule
  {\{B\mapsto resume\},
    b1=true \land b2=true \land b1=b2, 
    \{t:=0, z:=TopInt\} }
  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{11}}
  $
  \medskip

  $  OT_9  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\} }
  {\ostate{12} \OTarrow{\underline{\alpha_2}} \ostate{13}}
  $
  \medskip

  $  OT_{10}  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
    \{t:=t+1, z:=z1\} }
  {\ostate{13} \OTarrow{\underline{\alpha_0}} \ostate{13}}
  $
  \medskip

  $  OT_{11}  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{13} \OTarrow{\underline{\alpha_1}} \ostate{13}}
  $
  \medskip

  $  OT_{12}  = \openrule
  {\{E\mapsto reset\},
    true,
    \{\} }
  {\ostate{13} \OTarrow{\underline{\alpha_3}} \ostate{11}}
  $

>>>>

\noteLH{a pred is a g a post is a u (modified macros!)}
\renewcommand{\Pred}{g}
\renewcommand{\Post}{u}
The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes the actions of several holes, 
the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{defn:OpenTransitions}
	An \emph{open transition} over a
	set $J$ of holes  and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{	\beta_j^{j\in J}, \Pred, \Post}
	{s \OTarrow {{\alpha}}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
        is an action of the hole $j$. $v$ is a variable denoting the resulting action
        of this open transition. \Pred\ is a predicate 
	over the different variables of the
	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
	\assigns{\variables}$\ is 
	a set of assignments that are the effects of the transition.
Open transitions are identified modulo logical equivalence on their predicate.
\end{definition}
%\begin{definition}[Open transitions]
%	\label{def:OpenTransitions}
%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
%we omit indices on $\goesto{}$ and that they are always clear from the 
%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
%	I}$} of LTSs, a
%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
%	a structure of the form:	
%	\begin{mathpar}
%	\inferrule*[myfraction=\reddottedrule]
%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
%	{s \OTarrow {v}s'}
%	\end{mathpar}
%	Where $s, s'\in\mathcal{S}$ and for all
%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
%        is a transition of the hole $j$}, for any action $b_j$ in the
%        sort $\Sort_j$.  
%        of this open transition. \Pred\ is a predicate 
%	over the different variables of the
%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
%	hold \emph{after the open transition}, they are represented as a substitution of the 
%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
%	would like to just put $\Post_=e$}
%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
%	variables of the open transition.
%\end{definition}

\begin{example}\emph{An open-transition.}
  \label{Example:TimerOT3}

  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
  and 2 holes. One of its possible open-transitions is:

@@

  %% Removed to save space:
%%  \smallskip
%% $  OT_1  = \openrule
%% {\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%% {\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%% $
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  %  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
    {\ostate{11} \OTarrow{fail} \ostate{12}}
  $

\end{example}

@@

The second one, $OT_3$, correspond to the firing of the connector
$''tick, fail, fail''$, with the hole B performing action $fail$......

It is important to understand the difference between the red dotted rule and a normal 
inference rule. They correspond to two different logical levels.
 The open transition is itself a logical implication, but using a simple logic (with the 
 expressive power that is given to the predicate and necessary include logical 
 propositions and equality). We differentiate classical (black) inference rules that use 
 an expressive logic and are paper rules from open transition rules that use a simpler 
 logic, 
 will be embedded into automata transitions, and could typically be handled in a 
 mechanical way.

@@

%% \begin{figure}[t]
%%   \centering
%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
%%   \caption{The open Automaton of the Failure Monitor Architecture}
%%   \label{schema:ArchFailure:BIP}
%% \end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:OA}
\end{figure}

In Figure~\ref{schema:ArchFailure:OA} we show the full open automaton
obtained from our pNet. For reasons of space, we have not shown the
detail of the open transition, but only the assignement of state
variables, and the resulting action. You can find the full details in
Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one explained in Example
\ref{Example:TimerOT3} page \pageref{Example:TimerOT3}.

@@

\small\begin{verbatim}
FailureTimerArchi
--------------------
SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->fail,
                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
SV1 SVs: <cancel(b1), resume(b2), resume, _>-->resume, (b1=b2)
SV2 SVs: <timeout, timeout, _, ask>-->ask
SV3 SVs: <_, reset, _, reset>-->reset
SV4 SVs: <init, init, _, _>-->init
pLTS: Timer
- Transition: t0---init-->t1, { t := 0 z := TopInt}
- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
- Transition: t1---cancel(false)-->t1, {}
- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
- Variable: t, State: t1, Value(s) = 0,0,(t+1),
- Variable: z, State: t1, Value(s) = TopInt,z1,
pLTS: Failure
- Transition: s0---init-->s1, { zone := minZone,maxZone}
- Transition: s1---timeout-->s1, {}
- Transition: s1---resume(false)-->s1, {}
- Transition: s1---fail(zone, false)-->s1, {}
- Transition: s1---fail(zone, true)-->s2, {}
- Transition: s2---fail(zone, false)-->s2, {}
- Transition: s2---resume(false)-->s2, {}
- Transition: s2---resume(true)-->s1, {}
- Transition: s2---timeout-->s3, {}
- Transition: s3---fail(zone, false)-->s3, {}
- Transition: s3---resume(false)-->s3, {}
- Transition: s3---reset-->s1, {}
- Variable: zone, State: s1, Value(s) = minZone,maxZone,
Holes: B
Holes: E

INFO  BIPArchFailureTimerMax_LTF3 -
       {t0---init-->t1, s0---init-->s1},   {},  [true],
       {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----init----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----fail----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----fail----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)
         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----resume----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT5 ------------------------------------------------------------
        <t1_s1>-----ask----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----fail----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----resume----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
       {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----resume----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT9 ------------------------------------------------------------
        <t1_s2>-----ask----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----fail----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----resume----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
    OT12 ------------------------------------------------------
        <t1_s3>-----reset----><t1_s1>

@@

$  OT_1  = \openrule
{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
{\ostate{00} \OTarrow{init} \ostate{11}}
$
\medskip

$  OT_2  = \openrule
{\{B\mapsto fail(b0)\},\\
  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
  \{z:=z1\} }
{\ostate{11} \OTarrow{fail} \ostate{11}}
$
\medskip

  $  OT_3  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{fail} \ostate{12}}
  $
  \medskip

  $  OT_4  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2
    \{\}  }
  {\ostate{11} \OTarrow{resume} \ostate{11}}
  $
  \medskip

  $  OT_5  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\}  }
  {\ostate{11} \OTarrow{ask} \ostate{11}}
  $
  \medskip

  $  OT_6  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
    \{t:=t+1, z:=z1\} }
  {\ostate{12} \OTarrow{fail} \ostate{12}}
  $
  \medskip

  $  OT_7  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{12} \OTarrow{resume} \ostate{12}}
  $
  \medskip

  $  OT_8  = \openrule
  {\{B\mapsto resume\},
    b1=true \land b2=true \land b1=b2, 
    \{t:=0, z:=TopInt\} }
  {\ostate{12} \OTarrow{resume} \ostate{11}}
  $
  \medskip

  $  OT_9  = \openrule
  {\{E\mapsto ask\},
    t \in z,
    \{t:=t+1\} }
  {\ostate{12} \OTarrow{ask} \ostate{13}}
  $
  \medskip

  $  OT_{10}  = \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
    \{t:=t+1, z:=z1\} }
  {\ostate{13} \OTarrow{fail} \ostate{13}}
  $
  \medskip

  $  OT_{11}  = \openrule
  {\{B\mapsto resume\},
    b1=false \land b2=false \land b1=b2,
    \{\} }
  {\ostate{13} \OTarrow{resume} \ostate{13}}
  $
  \medskip

  $  OT_{12}  = \openrule
  {\{E\mapsto reset\},
    true,
    \{\} }
  {\ostate{13} \OTarrow{reset} \ostate{11}}
  $
